\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-10 manuscript.Rmd

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
#packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
```

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
r_refs("references.bib")
```

@@

                    graph [layout = dot,fontsize = 14]

                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                    fixedsize = true]

@@

                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
                    fixedsize = true]
                    C[label = 'Factor Identification
                    Scree Plot: 6 Factors
                    Parallel Analysis: 6 Factors
                    Minimum Average Partial Method: 5 Factors
                    Hull Method: 5 Factors']

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]

                     1[label = '5 Factor Solution Retained 23 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Alpha F1 =.49; F2 = .71; F3 = .86; F4 =.62; F5 =.77']

                     3[label = 'Confirmatory Factor Analysis on Modified Model
                     on the Five Factor Model (21 Items; N=199)
                      Acceptable Fit ( CFI = .92; TLI .91; RMSEA = .05, SRMR = .07)']

                     4[label = 'Reliability Analysis on CFA (N=199) 
                      Alpha F1=.47; F2=.67; F3 =.92; F4=.58; F5= .74']
                    }
                subgraph cluster_2 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
                    5[label = '6-Factor  one factor with only two salient loadings']
                    6[label = 'Rejected']
                    }

                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     C ->5
                     5 ->6

@@

@@

# Calculating the percentage of correlations higher than .30

@@

hist(residual.6F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 250))
abline(h =27, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
```

@@

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

@@

### CFA Data
CFA.data <- sem.data[429:690,]
CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem26 = recode(CFA.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
CFA.data <- CFA.data %>% 
  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)
```

@@

```{r tabCfa, results='asis'}
CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

CFa.matrix[2,] = c("Five factor model", 
                   apa(cfa.sum.2$FIT[6],2,T), 
                   apa(cfa.sum.2$FIT[7],2,T), 
                   apa(cfa.sum.2$FIT[19],2,F), 
                   apa(cfa.sum.2$FIT[20],2,T),
                   apa(cfa.sum.2$FIT[27],2,T),
                   apa(cfa.sum.2$FIT[28],2,T),
                   apa(cfa.sum.2$FIT[29],2,T),
                   apa(cfa.sum.2$FIT[35],2,T))

@@

F1.IRT.data <- sem.data %>% 
  select(item16, item36,  item17)

F2.IRT.data <- sem.data %>% 
  select(item16, item36,  item17)

>>>>

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
```

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
r_refs("references.bib")
```

@@

                    graph [layout = dot,fontsize = 20]

                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                    fixedsize = true,fontsize = 20]

@@

                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
                    fixedsize = true, fontsize = 20]
                    C[label = 'Factor Identification
                    Scree Plot: 6 Factors
                    Parallel Analysis: 6 Factors
                    Minimum Average Partial Method: 5 Factors
                    Hull Method: 5 Factors']

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true, fontsize = 18 ]

                     1[label = '5 Factor Solution Retained 25 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']

                     3[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (25 Items; N=262)
                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    }
                subgraph cluster_2 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
                    6[label = '6-Factor  one factor with only two salient loadings']
                    7[label = 'Rejected']
                    }

                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                     C ->6
                     6 ->7

@@

#Histogram
#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])

@@

determinets <- det(correlations$rho) 
# Calculating the percentage of correlations higher than .30

@@

hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
abline(h =65, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
```

@@

```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =51, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

@@

### CFA Data
CFA.data <- sem.data[429:690,]
CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem26 = recode(CFA.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
CFA.data <- CFA.data %>% 
  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)

#Hitogram
#psych::multi.hist(CFA.data[,sapply(CFA.data, is.numeric)])
```

@@

```{r tabCfa, results='asis'}
CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
CFa.matrix[1,] = c("Five factor model:25", 
                   apa(cfa.sum.1$FIT[6],2,T), 
                   apa(cfa.sum.1$FIT[7],2,T), 
                   apa(cfa.sum.1$FIT[19],2,F), 
                   apa(cfa.sum.1$FIT[20],2,T),
                   apa(cfa.sum.1$FIT[27],2,T),
                   apa(cfa.sum.1$FIT[28],2,T),
                   apa(cfa.sum.1$FIT[29],2,T),
                   apa(cfa.sum.1$FIT[35],2,T))

CFa.matrix[2,] = c("Five factor model:23", 
                   apa(cfa.sum.2$FIT[6],2,T), 
                   apa(cfa.sum.2$FIT[7],2,T), 
                   apa(cfa.sum.2$FIT[19],2,F), 
                   apa(cfa.sum.2$FIT[20],2,T),
                   apa(cfa.sum.2$FIT[27],2,T),
                   apa(cfa.sum.2$FIT[28],2,T),
                   apa(cfa.sum.2$FIT[29],2,T),
                   apa(cfa.sum.2$FIT[35],2,T))

@@

IRTitem8 = recode(sem.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTitem37 = recode(sem.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTitem26 = recode(sem.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
sem.data <- sem.data %>% 
  mutate(Ritem8 = IRTitem8, Ritem37 = IRTitem37, Ritem26 = IRTitem26)

F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)

F2 <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)

F3 <- sem.data %>% 
 dplyr::select(item27, item3,  item40,  item30,  item41)

F4 <- sem.data %>% 
 dplyr::select(item32, item35,  item38,  item33)

F5 <- sem.data %>% 
  dplyr::select(item46, item45, item25, item4, item1 )

## F1 IRT model####
F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
               SE = TRUE, Se.type = 'MHRM',
               technical = list(NCYCLES = 10000))

## F2 IRT model####
F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

## F3 IRT model####
F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

## F4 IRT model####
F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

## F5 IRT model####
F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

# Model Parameters ####
## F1 Model Parameters####
F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
F1_items <- data.frame(F1_params$items)
F1l_se <- coef(F1_fit, printSE = TRUE)

## F2 Model Parameters####
F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
F2_items <- data.frame(F2_params$items)
F2_se <- coef(F2_fit, printSE = TRUE)

## F3 Model Parameters####
F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
F3_items <- data.frame(F3_params$items)
F3_se <- coef(F3_fit, printSE = TRUE)

## F4 Model Parameters####
F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
F4_items <- data.frame(F4_params$items)
F4_se <- coef(F4_fit, printSE = TRUE)

## F5 Model Parameters####
F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
F5_items <- data.frame(F5_params$items)
F5_se <- coef(F5_fit, printSE = TRUE)

# Person Fit ####
## F1 Person fit ####
F1.personfit <- personfit(F1_fit) 
F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
rownames(F1.personfit_model_misfits)
nrow(F1.personfit_model_misfits)
hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

## F2 Person fit ####
F2.personfit <- personfit(F2_fit) 
F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
rownames(F2.personfit_model_misfits)
nrow(F2.personfit_model_misfits)
hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

## F3 Person fit ####
F3.personfit <- personfit(F3_fit) 
F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
rownames(F3.personfit_model_misfits)
nrow(F3.personfit_model_misfits)
hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

## F4 Person fit ####
F4.personfit <- personfit(F4_fit) 
F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
rownames(F4.personfit_model_misfits)
nrow(F4.personfit_model_misfits)
hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

## F5 Person fit ####
F5.personfit <- personfit(F5_fit) 
F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
rownames(F3.personfit_model_misfits)
nrow(F5.personfit_model_misfits)
hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

# Item Fit ####

## F1 Item Fit ####
F1_itemfit <- itemfit(F1_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

F1.missfit <- F1_itemfit[F1_itemfit$p.S_X2 < 0.05, ]

## F2 Item Fit ####
F2_itemfit <- itemfit(F2_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F2.missfit <- F2_itemfit[F2_itemfit$p.S_X2 < 0.05, ]

## F3 Item Fit ####
F3_itemfit <- itemfit(F3_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F3.missfit <- F3_itemfit[F3_itemfit$p.S_X2 < 0.05, ]

## F4 Item Fit ####
F4_itemfit <- itemfit(F4_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F4.missfit <- F4_itemfit[F4_itemfit$p.S_X2 < 0.05, ]

## F5 Item Fit ####
F5_itemfit <- itemfit(F5_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
                      impute=10)

F5.missfit <- F5_itemfit[F5_itemfit$p.S_X2 < 0.05, ]

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", main = "Blue Filter Item Information")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", main = "Natural Light Item Information")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", main = "Smart Device Item Information")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", main = "Sleep Environment Item Information")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", main = "Electric Light Item Information")

## Plot grid ####
library(cowplot)
plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
